humanCdGF_predict_cfu

### 2016-11-08 code/HumanCdGF_predict_cfu.Rmd
add partial plot for one mouse model

OTUS <- unique(as.character(om_pp$otu))
part_plot_cfu <- c()
for(i in OTUS){
om_v_oob <- rbind(data.frame(model = 'OM',
                             om_pp[om_pp$otu == i, ]),
                  data.frame(model = 'OOB', otu = i,
                             partialPlot(rf_n_features, data.frame(cfu_shared_colonized.df), 
                                         OTUS[OTUS == i], plot = F)))
part_plot_cfu[[i]] <- list(ggplot(om_v_oob, aes(x,y, group = model, color = model)) +geom_smooth() + geom_point(alpha = 0.5) + ggtitle(i))
}
part_plot_cfu[1]
part_plot_cfu[2]
part_plot_cfu[3]

>>>>

OTUS <- unique(as.character(om_pp$otu))
part_plot_cfu <- c()
for(i in OTUS){
om_v_oob <- rbind(data.frame(model = 'OM',
                             om_pp[om_pp$otu == i, ]),
                  data.frame(model = 'OOB', otu = i,
                             partialPlot(rf_n_features, data.frame(cfu_shared_colonized.df), 
                                         OTUS[OTUS == i], plot = F)))
gg_pp <- ggplot(om_v_oob, aes(x,y, group = model, color = model)) +geom_smooth() + ggtitle(i)
part_plot_cfu[[i]] <- gg_pp
}
library(cowplot)

ggdraw() + 
  draw_plot(part_plot_cfu[[1]])
plot_grid(part_plot_cfu[[1]], part_plot_cfu[[2]])

do.call('plot_grid',part_plot_cfu)
i <- 'Otu000004'
plot(om_pp$x[om_pp$otu == i], om_pp$y[om_pp$otu == i])
lines(lowess(om_pp$x[om_pp$otu == i], om_pp$y[om_pp$otu == i]))
library(car)
scatterplot(y~x, om_pp[om_pp$otu == i, ], spread = F, smoother = gamLine,
            grid = F, lty = 0)
